---
title: "Network Analytics Package"
author: "Fan Ouyang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This is a simple package of three core functions of network analytics I used as a part of my dissertation. This introduction includes four parts:
- Overview of the data
- Plot network sociograph function
- Calculate node-level measures function
- Calculate network-level measures function
- Other info

## Overview of the data

My dissertation focused on social learning analytics of a graduate-level 14-week semester-long online course. I only included four weeks' data in this package, i.e., week 02, week 08, week 13 and week 14. Each weekly data included two format: a network-format data (e.g., week02_network) and an adjacent-matrix data (e.g., week02_matrix). The network-format data includes attributes for the network, vertex and edge of the network. The adjacent-matrix data shows a square-format who-reply-to-whom matrix.

## Function 01: Plot network sociograph 

This function plots sociograph for a network in fruchtermanreingold mode, with node size and color representing a participant's degree (indegree and outdegree) and edge width representing the frequency of interactions between two participants. An example: sna_plot(week02_network,week02_matrix)

```{r eval=F, echo=T}
networkanalyticspackage::sna_plot(week02_network,week02_matrix)
```


## Function 02: Node-level measures of participants in a network

This function returns a network's node-level measures, namely every participant's in/outdegree, betweenness, closeness. An example: node_measure(week02_network)

```{r eval=F, echo=T}
networkanalyticspackage::node_measure(week02_network)
```


## Function 03: Network-level measures of a network

This function returns results of a network's network-level measures, including network size, density,
average degree, number of edges, reciprocity, transitivity, centralization, hierarchy,
number of components, connectedness. An example: network_measure(week02_network)

```{r eval=F, echo=T}
networkanalyticspackage::network_measure(week02_network)
```

## Other info

More info please go to another github repo: https://github.com/fanouyang/sna_exampler, demonstrating basic concepts, examples, Shiny app, original research paper, and a short intro video.
